Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms \thanks{This work was supported by a private funding of Velbazhd Software LLC.}

### 2019-01-12 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Small part of the introduction section was added.

\section{First Section}

@@

\cite{ref_author1}
\cite{ref_author2}
\cite{ref_author3,ref_author4}

\begin{thebibliography}{8}
\bibitem{ref_author1}
Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)

\bibitem{ref_author2}
Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)

>>>>

\section{Introduction}

A parallel implementation of a genetic algorithm based solver of the Rubik's cube was implemented by Balabanov in \cite{balabanov01} and it was presented in \cite{balabanov02}. Rubik's cube was invented and introduced by Erno Rubik in the 70s of the 20th century. After its creation the cube became the most popular combinatorial puzzle all over the world. In its original version it has 3x3x3 cubical segments.

@@

\section{Conclusions}

\cite{ref_author3,ref_author4}

\begin{thebibliography}{8}
\bibitem{balabanov01}
MPI Parallel Implementation of Genetic Algorithm Based Rubik’s Cube Solver, \url{http://github.com/TodorBalabanov/RubiksCubeGeneticAlgorithmsSolver}. Last accessed 12 Jan 2019
\bibitem{balabanov02}
Balabanov, T., Zankinski, I., Barova, M.: Strategy for Individuals Distribution by Incident Nodes Participation in Star Topology of Distributed Evolutionary Algorithms. Cybernetics and Information Technologies \textbf{16}(1), 80--88 (2016)
